Unsupervised embedding of trajectories captures the latent structure of mobility

### 2021-01-21 paper/current/main.tex
first edit in the Methods

Due to the negative sampling, the correct expression optimized with the negative sampling is given by (see Methods:Skip-gram and \textit{word2vec})
\begin{align}
	P\left(j \given i \right):= \frac{p_0(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z'_i},
\end{align}
where $Z'_i=\sum_{x \in \mathcal{A}} p_0(x) \exp(\bm{u}_{x} \cdot \bm{v}_{i})$.

@@

\subsection*{Skip-gram and \textit{word2vec}}
\label{sec:sg_and_word2vec}
Many probability models including the \textit{word2vec} can be represented in form
\begin{align}
	f(x) / \sum_{x' \in {\cal X}} f(x'),
\end{align}
where $f$ is a nonnegative function. Fitting the probability models are computationally expensive as its denominator involves a sum over all possible entities ${\cal X}$ in data.
The negative sampling is introduced as a way to avoid computing the denominator.
The negative sampling solves a synthetic binary classification task, classifying an actual data $x$ and a noise data $\tilde x$ using a sigmoid function
\begin{align}
	\label{eq:sigmoid}
	\frac{1}{1 + \exp\left( -\log f(z) \right)}.
\end{align}
Because this sigmoid function does not involve the normalization constant, the model fitting can be done with less computational burden. Besides , this has a side effect: the negative sampling has a bias and hence does not correctly train the model \cite{Dyer2014}.
The bias can be corrected using the noise contrastive estimation (NCE) \cite{Chia2010}, which solves the
same classification task but with a bias-corrected sigmoid function, \ie
\begin{align}
	\label{eq:sigmoid2}
	\frac{1}{1 + \exp\left( -\log f(z) + \log p_0(z) \right)}.
\end{align}
Note that Eq.~\eqref{eq:sigmoid2} has an additional term $\log p_0(z)$, which is the log-probability of $z$ for a noise distribution.

>>>>

Due to the negative sampling, the correct expression optimized with the negative sampling is given by
\begin{align}
	P\left(j \given i \right):= \frac{P(j)\exp(\bm{u}_j \cdot \bm{v}_{i})}{Z_i},
\end{align}
where $Z_i=\sum_{j' \in \mathcal{A}} P(j') \exp(\bm{u}_{j'} \cdot \bm{v}_{i})$.

@@

\subsection*{Skip-gram and \textit{word2vec}}
\label{sec:sg_and_word2vec}

The \textit{word2vec} takes a form
\begin{align}
	\frac{ f(\bm{u}_{j'}, \bm{v}_i) }{ \sum_{j' \in {\cal A}} f(\bm{u}_{j'}, \bm{v}_i)},
\end{align}
where $f$ is a nonnegative function.
Fitting the probability model is computationally expensive as its denominator involves a sum over all possible entities ${\cal A}$ in data.
To circumvent this problem, the negative sampling solves a binary classification task,
in which one is given an instance $z$ and asked whether $z$ is sampled from an actual data $x$ or a noise data $\tilde x$,
\begin{align}
	\label{eq:sigmoid}
	\frac{1}{1 + \exp\left( -\log f(z) \right)}.
\end{align}
Because this sigmoid function does not involve the normalization constant, the model fitting can be done with less computational burden. Besides, this has a side effect: the negative sampling has a bias and hence does not correctly train the model \cite{Dyer2014}.
The bias can be corrected using the noise contrastive estimation (NCE) \cite{Chia2010}, which solves the
same classification task but with a bias-corrected sigmoid function, \ie
\begin{align}
	\label{eq:sigmoid2}
	\frac{1}{1 + \exp\left( -\log f(z) + \log p_0(z) \right)}.
\end{align}
Note that Eq.~\eqref{eq:sigmoid2} has an additional term $\log p_0(z)$, which is the log-probability of $z$ for a noise distribution.
